---
title: "Cross Validation"
output: github_document
author: David Nemirovsky
---

```{r setup, include = F}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 7,
  fig.asp = .6,
  out.width = "95%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

## Simulate data

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

## Cross-validation by hand

Get training and testing datasets:

```{r}
train_df = sample_n(nonlin_df, 80)
test_df = anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

Fit three models:

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

Can I see what I just did?

```{r}
train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_wrap(~model)
```

Look at prediction accuracy:

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

## Cross Validation using `modelr`

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100)
```

What is happening here?

```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble()
cv_df %>% pull(test) %>% .[[1]] %>% as_tibble()
```

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

Let's try to fit models and get RMSEs in them:

```{r}
cv_df =  
  cv_df %>% 
  mutate(
    linear_mod  = map(train, ~lm(y ~ x, data = .x)),
    smooth_mod  = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
    wiggly_mod  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y)))
```

What do these results say about model choice?

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

Compute averages:

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  group_by(model) %>% 
  summarize(avg = mean(rmse))
```

## Try on a real dataset

```{r}
child_growth = 
  read_csv("./nepalese_children.csv") %>% 
  mutate(weight_cp = (weight > 7) * (weight - 7))
```

weight vs arm circumference

```{r}
child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = 0.3)
```

Fit the models I care about:

```{r}
linear_mod = lm(armc ~ weight, data = child_growth)
pwl_mod    = lm(armc ~ weight + weight_cp, data = child_growth)
smooth_mod = gam(armc ~ s(weight), data = child_growth)
```

```{r}
child_growth %>% 
  gather_predictions(linear_mod, pwl_mod, smooth_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5) +
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(~model)
```

Try to understand model fit using CV:

```{r}
cv_df =
  crossv_mc(child_growth, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

Se if I can fit the models to the splits:

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    linear_mod  = map(train, ~lm(armc ~ weight, data = .x)),
    pwl_mod     = map(train, ~lm(armc ~ weight + weight_cp, data = .x)),
    smooth_mod  = map(train, ~gam(armc ~ s(weight), data = as_tibble(.x)))) %>% 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
    rmse_pwl    = map2_dbl(pwl_mod, test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)))
```

Violin plots of RMSEs:

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

Pick the piece-wise b/c it's easier to explain!