---
title: "Linear Models"
output: github_document
author: David Nemirovsky
---

```{r setup, include = F}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 7,
  fig.asp = .6,
  out.width = "95%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

Import data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

## Fit a model

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, colour = borough)) + 
  geom_point()
```

Let's fit a model and look at the results:

```{r, include = F}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
resid(fit)
```

Let's look at the results better:

```{r}
broom::glance(fit)
broom::tidy(fit) %>% 
  select(-std.error, -statistic) %>% 
  mutate(term = str_replace(term, "borough", "Borough: ")) %>% 
  knitr::kable(digits = 3)
```

## Be in control of factors

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough), 
    room_type = fct_infreq(room_type)
  )
```

Let's look at the plot again:

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, colour = borough)) + 
  geom_point()
```

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

broom::tidy(fit)
```

## Diagnostics

```{r}
#residuals against boroughs
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = borough, y = resid)) + 
  geom_violin() +
  ylim(-500, 1500)

# residuals against predictors
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) + 
  geom_point() +
  facet_wrap(. ~ borough)
```

## Hypothesis tests

This does t-tests by default:

```{r}
fit %>% 
  broom::tidy()
```

But what about the significance of borough?

```{r}
fit_null = lm(price ~ stars, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```

## Nest data, fit models

This is pretty formal and more complex:

```{r}
lm(price ~ stars * borough + room_type * borough, data = nyc_airbnb) %>% 
  broom::tidy()
```

This is more exploratory but maybe easier to understand:

```{r}
nyc_airbnb %>% 
  nest(data = -borough) %>% 
  mutate(
    models = map(.x = data, ~ lm(price ~  stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-data, -models) %>% 
  unnest() %>% 
  filter(term != "(Intercept") %>% 
  select(borough, term, estimate) %>% 
  pivot_wider(
    names_from = borough,
    values_from = estimate
  )
```

Let's nest even more:

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(. ~ term) + 
  theme(axis.text.x = element_text(angle = 65, vjust = 0.5, hjust = 1))
```

